Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-09 ccppabc/text/revision/main.tex
continuing edits on Section 3.4

{\bf \color{dred} 
Although in our comparison using simple mock observations, we find generally 
consistent parameter constraints from both the ABC-PMC analysis and the standard 
Gaussian pseudo-likelihood analysis, more realistic scenarios face mmany factors
that can generate inconsistencies. Consider a typical galaxy catalog from 
observations for LSS. These catalogs consist of objects with different data 
qualities, signal-to-noise ratios, and systematic effects. For example, catalogs 
are often incomplete beyond some luminosity/redshift or have some threshold 
signal-to-noise ratio cut imposed on them.
}

%It is possible to consider a scenario in which the results from the standard analysis are inconsistent with the results from the ABC.  Let us consider a dataset---from a galaxy survey---consisting of objects with different data qualities, signal-to-noise ratios, and systematic effects.  This could be a catalog of galaxies which is incomplete beyond a certain luminosity or redshift. Another example could be a catalog with a signal-to-noise ratio cut.
{\bf \color{dred} 
These selection effects, coupled with the systematic effects mentioned above, 
make correctly predicting the functional form of the likelihood difficult. 
In the standard Gaussian pseudo-likelihood analysis, and other analysis that
depend on writing down a likelihood function, these effects can siginficantly 
bias the inferred parameters of interest. In these situations, employing
ABC equipped with a generative forward model that incorproates selection and 
systematic effects may produce less biased parameter constraints. 
}
%Methods that rely on a likelihood function may not correctly predict how the functional form of the likelihood is impacted by the presence of possible selection effects and systematic uncertainties.  
%Alternatively, one could alleviate this issue by employing ABC equipped with a generative forward model of the simulated data that incorporates signal-to-noise ratio cuts, incompleteness, systematic uncertainties etc. }{
%\bf \color{darkgreen} MJV: @CHH Can you read the two paragraphs above and see if they address referee's concern about the extreme data situation that could lead to discrepancy ? }
%%%
%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood 
%MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using 
%ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, 
%accounts for sample variance. In principle, they also have the advantage that they can account for 
%sources of systematic uncertainties in the observational data.

>>>>

{\bf \color{dred} 
Although in our comparison using simple mock observations, we find generally 
consistent parameter constraints from both the ABC-PMC analysis and the standard 
Gaussian pseudo-likelihood analysis, more realistic scenarios present many factors
that can generate inconsistencies. Consider a typical galaxy catalog from 
LSS observations. These catalogs consist of objects with different data 
qualities, signal-to-noise ratios, and systematic effects. For example, catalogs 
are often incomplete beyond some luminosity/redshift or have some threshold 
signal-to-noise ratio cut imposed on them.
}

%It is possible to consider a scenario in which the results from the standard analysis are inconsistent with the results from the ABC.  Let us consider a dataset---from a galaxy survey---consisting of objects with different data qualities, signal-to-noise ratios, and systematic effects.  This could be a catalog of galaxies which is incomplete beyond a certain luminosity or redshift. Another example could be a catalog with a signal-to-noise ratio cut.
{\bf \color{dred} 
These selection effects, coupled with the systematic effects earlier this section, 
make correctly predicting the functional form of the likelihood intractable.
In the standard Gaussian pseudo-likelihood analysis, and other analysis that
require writing down a likelihood function, these effects can significantly 
bias the inferred parameter constraints. In these situations, employing
ABC equipped with a generative forward model that incorproates selection and 
systematic effects may produce less biased parameter constraints. 
}
%Methods that rely on a likelihood function may not correctly predict how the functional form of the likelihood is impacted by the presence of possible selection effects and systematic uncertainties.  
%Alternatively, one could alleviate this issue by employing ABC equipped with a generative forward model of the simulated data that incorporates signal-to-noise ratio cuts, incompleteness, systematic uncertainties etc. }{
%\bf \color{darkgreen} MJV: @CHH Can you read the two paragraphs above and see if they address referee's concern about the extreme data situation that could lead to discrepancy ? }
%%%
%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood 
%MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using 
%ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, 
%accounts for sample variance. In principle, they also have the advantage that they can account for 
%sources of systematic uncertainties in the observational data.
